---
title: "TD2"
author: "Paul Géraud"
date: "2024-02-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(ggforce)
library(gridExtra)
```

# Exercice 3

Simulate prices
```{r}
#parameters
Monte_Carlo_Price=function(S_0,sigma,T,r,nbr_traj)
{
  Z=rnorm(nbr_traj)
  S_T=S_0*exp((r-sigma^2/2)*T+sigma*sqrt(T)*Z)
  return(S_T)
}

n=10^6
S_0=100
sigma=0.2
r=0.01
T=0.5
S_T=Monte_Carlo_Price(S_0,sigma,T,r,n)
```
Average price
```{r}
mean(S_T)
```
Get Calls
```{r}
Price_Call=function(S_T,K)
{
  C_T=pmax(S_T-K,0)
  return (C_T)
}
K=100
C_T=Price_Call(S_T,K)
```
Mean Call price
```{r}
mean(C_T)
```
Now let's do it with Strikes being different multiple of S_0
```{r}
Ks=S_0*seq(from=0.5,to=1.3,by=0.1)
Cs=rep(0,length.out=9)
sdS=rep(0,length.out=9)
for(i in 1:9)
{
  placeholder=Price_Call(S_T,Ks[i])
  Cs[i]=mean(placeholder)
  sdS[i]=sd(placeholder)/sqrt(n)
}
print(Cs)
```
```{r}
print(sdS)
```

Get Confidence boundaries
```{r}
bound=qnorm(0.005)*exp(r*T)*(exp(T*sigma^2)-1)/sqrt(n)
```

Compare to Black Scholes formula
```{r}
d1s=(log(S_0/Ks)+(r+sigma^2/2)*T)/(sigma*sqrt(T))
d2s=d1s-sigma*sqrt(T)
C_BS=pnorm(d1s)*S_0-pnorm(d2s)*Ks*exp(-r*T)
print(C_BS)
```
On retrouve des résultats similaires

# Exercice 4

## Controle variate method
```{r}
MonteCarlo_Control=function(S_0,sigma,T,r,K,nbr_traj)
{
  Z=rnorm(nbr_traj)
  S_T=S_0*exp((r-sigma^2/2)*T+sigma*sqrt(T)*Z)
  C_T=pmax(S_T-K,0)
  Beta=cov(S_T,C_T)/var(S_T)
  Control_Ct=C_T-Beta*(S_T-mean(S_T))
  return(Control_Ct)
}
```

Let's do it again for a different range of strikes:
```{r}
Ks=S_0*seq(from=0.5,to=1.3,by=0.1)
CsControl=rep(0,length.out=9)
sdSControl=rep(0,length.out=9)
for(i in 1:9)
{
  placeholder=MonteCarlo_Control(S_0,sigma,T,r,Ks[i],n)
  CsControl[i]=mean(placeholder)
  sdSControl[i]=sd(placeholder)/sqrt(n)
}
print(CsControl)
```
```{r}
print(sdSControl)
```
We find similar results but we can observe indeed that the variance has been reduced

## Importance sampling method

```{r}
drift=30 #valeur à modifier
S_T_drift=S_T+drift
plot(density(S_T_drift),ylim=c(0,0.5))
#hist(S_T_drift,breaks=sqrt(length(S_T_drift)))
# graphe payoff call strike K
K=130
t=seq(0,150,length.out=1000)
c=pmax(t-K,0)
lines(t,c,col="red")

```
Générons nos calls pour ce strike de 130 avec ce drift:
```{r}
C_T_importance=pmax(S_T_drift-K,0)
cat("Moyenne: ",mean(C_T_importance),"\nEcart Type: ",sd(C_T_importance)/sqrt(n))
```
Résultats imparfaits. Il faut modifier quelque chose

# Exercice 6

## Implémentation Van der Corput
```{r}
RepresBase_b=function(k,b)
{
  
  if(k!=0)
  {
    #il faut obtenir le nombre de chiffres nécessaires pour écrire k en base b
    nbr_chiffres=0
    while(k>=b^nbr_chiffres)
    {
      nbr_chiffres=nbr_chiffres+1
    }
    #Créer liste coeffs
    a_k=rep(0,nbr_chiffres)
    for (i in nbr_chiffres:1)
    {
      a_k[i]=k%/%b^(i-1)
      k=k-a_k[i]*b^(i-1)
    }
  }
  else
  {
    a_k=0
  }
  return(a_k)
}
```
Let's compute now the kth term of the Van der Corput serie
```{r}
Van_der_Corput_kth=function(k,b)
{
  #obtenir la représentation de k en base b
  a=RepresBase_b(k,b)
  VdC=0
  for(i in 1:length(a))
  {
    VdC=VdC+a[i]/b^(i)  
  }
  return (VdC)
}
```
Exemples
```{r}
Van_der_Corput_kth(6,100)
```

## Representation base b nombre suivant

```{r}
NombreSuivant=function(a,b)
{
  n=length(a)
  for(i in n:1)
  {
    if(a[i]<b-1)
    {
        a[i]=a[i]+1
        break;
    }
    else
    {
      a[i]=0
      if(i-1!=0)
      {
        a[i-1]=a[i-1]+1
      }
      else
      {
        a=c(1,a)
      }
      
    }
  }
  return(a)
}
```

##Calculer les premiers nombres sequences van der Corput
```{r}
k_first_VDC=function(k,b)
{
  vdc=rep(0,k)
  num=NombreSuivant(0,b)
  
  for(i in 1:k)
  {
    vdc[i]=Van_der_Corput_kth(num,b)
    VdC=0
    for(j in 1:length(num))
    {
      VdC=VdC+num[j]/b^(length(num)-j+1)  
    }
    vdc[i]=VdC
    num=NombreSuivant(num,b)
    print(num)
  }
  return(vdc)
}
```



```{r,warning=FALSE}
test=k_first_VDC(20,2)
print(test)
```

## Application Quasi Monte Carlo
```{r}
QuasiMC_Price=function(base,S_0,sigma,T,r,nbr_traj)
{
  seq=k_first_VDC(nbr_traj,base)
  Z=qnorm(seq)
  S_T=S_0*exp((r-sigma^2/2)*T+sigma*Z*sqrt(T))
  return(S_T)
}
```

```{r,warning=FALSE}
n=1000
S_0=100
sigma=0.2
r=0.01
T=0.5
K=100
S_T=QuasiMC_Price(2,S_0,sigma,T,r,n)
C_T=Price_Call(S_T,K)
mean(C_T)


```
```{r}
S_T=Monte_Carlo_Price(S_0,sigma,T,r,n)
C_T=Price_Call(S_T,K)
mean(C_T)
```



